\documentclass[11pt]{article}

%% MinionPro fonts 
%\usepackage[lf]{MinionPro}
%\usepackage{MnSymbol}
\usepackage{microtype}

%% Margins
\usepackage{geometry}
\geometry{verbose,letterpaper,tmargin=1in,bmargin=1in,lmargin=1in,rmargin=1in}

%% Other packages
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage[shortlabels]{enumitem}
\usepackage{titlesec}
\usepackage{soul}
\usepackage{tikz}
\usepackage{mathtools}
\usepackage{pgfplots}
\usepackage{tikz-3dplot}
\usepackage{algorithmic}
\usepackage[export]{adjustbox}
\usepackage{tcolorbox}
\usepackage{optprog}
\usepackage{amsfonts}
\usepackage{pdfpages}

%% Paragraph style settings
\setlength{\parskip}{\medskipamount}
\setlength{\parindent}{0pt}

%% Change itemize bullets
\renewcommand{\labelitemi}{$\bullet$}
\renewcommand{\labelitemii}{$\circ$}
\renewcommand{\labelitemiii}{$\diamond$}
\renewcommand{\labelitemiv}{$\cdot$}

%% Colors
\definecolor{rred}{RGB}{204,0,0}
\definecolor{ggreen}{RGB}{0,145,0}
\definecolor{yyellow}{RGB}{255,185,0}
\definecolor{bblue}{rgb}{0.2,0.2,0.7}
\definecolor{ggray}{RGB}{190,190,190}
\definecolor{ppurple}{RGB}{160,32,240}
\definecolor{oorange}{RGB}{255,165,0}

%% Shrink section fonts
\titleformat*{\section}{\normalsize\bf}
\titleformat*{\subsection}{\normalsize\bf}
\titleformat*{\subsubsection}{\normalsize\it}

% %% Compress the spacing around section titles
\titlespacing*{\section}{0pt}{1.5ex}{0.75ex}
\titlespacing*{\subsection}{0pt}{1ex}{0.5ex}
\titlespacing*{\subsubsection}{0pt}{1ex}{0.5ex}

%% amsthm settings
\theoremstyle{definition}
\newtheorem{problem}{Problem}
\newtheorem{example}{Example}
\newtheorem*{theorem}{Theorem}
\newtheorem*{bigthm}{Big Theorem}
\newtheorem*{biggerthm}{Bigger Theorem}
\newtheorem*{bigcor1}{Big Corollary 1}
\newtheorem*{bigcor2}{Big Corollary 2}

%% tikz settings
\usetikzlibrary{calc}
\usetikzlibrary{patterns}
\usetikzlibrary{decorations}
\usepgfplotslibrary{polar}


%% algorithmic setup
\algsetup{linenodelimiter=}
\renewcommand{\algorithmiccomment}[1]{\quad// #1}
\renewcommand{\algorithmicrequire}{\emph{Input:}}
\renewcommand{\algorithmicensure}{\emph{Output:}}

%% Answer box macros
%% \answerbox{alignment}{width}{height}
\newcommand{\answerbox}[3]{%
  \fbox{%
    \begin{minipage}[#1]{#2}
      \hfill\vspace{#3}
    \end{minipage}
  }
}

%% \answerboxfull{alignment}{height}
\newcommand{\answerboxfull}[2]{%
  \answerbox{#1}{6.38in}{#2} 
}

%% \answerboxone{alignment}{height} -- for first-level bullet
\newcommand{\answerboxone}[2]{%
  \answerbox{#1}{6.0in}{#2} 
}

%% \answerboxtwo{alignment}{height} -- for second-level bullet
\newcommand{\answerboxtwo}[2]{%
  \answerbox{#1}{5.8in}{#2}
}

%% special boxes
\newcommand{\wordbox}{\answerbox{c}{1.2in}{.7cm}}
\newcommand{\catbox}{\answerbox{c}{.5in}{.7cm}}
\newcommand{\letterbox}{\answerbox{c}{.7cm}{.7cm}}

%% Miscellaneous macros
\newcommand{\tstack}[1]{\begin{multlined}[t] #1 \end{multlined}}
\newcommand{\cstack}[1]{\begin{multlined}[c] #1 \end{multlined}}
\newcommand{\ccite}[1]{\only<presentation>{{\scriptsize\color{gray} #1}}\only<article>{{\small [#1]}}}
\newcommand{\grad}{\nabla}
\newcommand{\ra}{\ensuremath{\rightarrow}~}
\newcommand{\maximize}{\text{maximize}}
\newcommand{\minimize}{\text{minimize}}
\newcommand{\subjectto}{\text{subject to}}
\newcommand{\trans}{\mathsf{T}}
\newcommand{\bb}{\mathbf{b}}
\newcommand{\bx}{\mathbf{x}}
\newcommand{\bc}{\mathbf{c}}
\newcommand{\bd}{\mathbf{d}}
\newcommand{\blu}{\color{blue}}
%% LP format
%    \begin{align*}
%      \maximize \quad & \mathbf{c}^{\trans} \mathbf{x}\\
%      \subjectto \quad & A \mathbf{x} = \mathbf{b}\\
%                       & \mathbf{x} \ge \mathbf{0}
%    \end{align*}


%% Redefine maketitle
\makeatletter
\renewcommand{\maketitle}{
  \noindent SA405 -- AMP 

  \begin{center}\Large{\textbf{\@title}}\end{center}
}
\makeatother

%% ----- Begin document ----- %%
\begin{document}

\begin{large}
\begin{center}
\textbf{HW 5: Unsymmetric Traveling Salesperson problem}
\end{center}
\end{large}

The TSP problem we did in class operated on an undirected graph; thus, an edge like $(1,2)$ can be from node 1 to node 2 or node 2 to node 1. In this homework problem, we will consider the unsymmetric traveling salesperson problem which operates on a directed graph (thus edge $(1,2)$ and $(2,1)$ are distinct).

\begin{problem}
Cameron is taking a vacation to New York City and wants to drive around to see some of the famous landmarks there. There are 8 total landmarks he wants to see. Since many of the roads in NYC are one way only, the path between two landmarks is not the same distance. The matrix below gives the distances (in miles) between each of the 8 landmarks he wants to visit.

\[
D = 
\begin{bmatrix}
0 & 2 & 3 & 1 & 7 & 5 & 4 & 4\\
1 & 0 & 3 & 2 & 4 & 2 & 6 & 3\\
2 & 1 & 0 & 4 & 2 & 4 & 7 & 1\\
3 & 2 & 1 & 0 & 4 & 3 & 2 & 2\\
6 & 8 & 1 & 2 & 0 & 4 & 6 & 5\\
3 & 2 & 4 & 2 & 7 & 0 & 3 & 4\\
2 & 3 & 1 & 4 & 5 & 6 & 0 & 2\\
1 & 4 & 3 & 2 & 7 & 4 & 3 & 0
\end{bmatrix}
\]

He wants to visit all of the landmarks while driving as little as possible and he asks you for help.
\end{problem}

\begin{enumerate}
\item Formulate a concrete model whose solution will give Cameron a tour that visits all 8 landmarks exactly once. \emph{Hint: Do not write all the subtour elimination constraints, you can write one or two then move on. Also, if you're having trouble getting started draw out the network for the problem.}

{\blu
\textbf{\underline{Decision Variables}}

Let $x_{1,2} = 1$ if edge $(1,2)$ is selected as part of the tour and 0 otherwise \\
$\vdots$ \\
Let $x_{8,7} = 1$ if edge $(8,7)$ is selected as part of the tour and 0 otherwise \\

\textbf{\underline{Objective Function}}

\[
\text{minimize: } 2 x_{1,2} + 3 x_{1,3} + \cdots + 6 x_{8,7}
\]

\textbf{\underline{Constraints}}

We have the typical constraints here, but notice that the big difference is that in a directed graph, you can have a cycle on only 2 nodes.

\begin{optprog*}
st & x_{1,2} + x_{1,3} + \cdots + x_{8,7} & = & 8 & \text{(can only take 8 edges for a tour)} \\
   & x_{1,2} + x_{1,3} + \cdots + x_{8,1} & = & 2 & \text{(node 1 is visited once)} \\
   & \vdots  & \vdots & \\
   & x_{1,8} + x_{2,8} + \cdots + x_{8,7} & = & 2 & \text{(node 8 is visited once)} \\
   & x_{1,2} + x_{2,1} & \leq & 1 & \text{(Subtour elim for nodes 1,2)} \\
   & x_{1,3} + x_{3,1} & \leq & 1 & \text{(Subtour elim for nodes 1,3)} \\
   & \text{and so on for all subtour elim} \\
   & x_{1,2}, x_{1,3}, \cdots , x_{8,7} & \in & \{0,1\} & \text{(binary)}
\end{optprog*}

}


\item Convert your concrete model above to a parameterized model.

{\blu

\textbf{\underline{Sets}}

Let $N$ be the set of nodes \\
Let $E$ be the set of edges

\textbf{\underline{Decision Variables}}

Let $x_{i,j} = 1$ if edge $(i,j)$ is included in the tour and 0 otherwise for all $(i,j) \in E$

\textbf{\underline{Parameters}}

Let $d_{i,j}$ be the length/distance of edge $(i,j)$ for all $(i,j) \in E$

\textbf{\underline{Objective Function}}

\[
\text{minimize: } \sum_{(i,j) \in E} d_{i,j} x_{i,j}
\]

\textbf{\underline{Constraints}}

We have the typical constraints here, but notice that the big difference is that in a directed graph, you can have a cycle on only 2 nodes.

\begin{optprog*}
st & \sum_{(i,j) \in E} x_{i,j} & = & |N| && \text{($|N|$ edges in a tour)} \\
   & \sum_{(i,n) \in E} x_{i,n} + \sum_{(n,j) \in E} x_{n,j} & = & 2 & \text{ for all $n \in N$} & \text{(each node visited once)} \\
   & \sum_{(i,j) \in E: i \in S, j \in S} x_{i,j} & \leq & |S| - 1 & \text{ for all $S \subset N$ $|S| \geq 2$} & \text{(subtour elim)} \\
   & x_{i,j} & \in & \{0,1\} & \text{ for all $(i,j) \in E$} & \text{(binary)}
\end{optprog*}

}



\item Suppose after solving your model, the solver returns the following solution. 

\verb|The following edges should be selected: (1,6), (2,1), (3,7), (4,3),| 

\verb|(5,2), (6,5), (7,8), (8,4)|
	\begin{enumerate}
	\item What are the values of your variables associated with this solution?
	{
	\blu
	\[
	x_{1,6} = x_{2,1} = x_{3,7} = x_{4,3} = x_{5,2} = x_{6,5} = x_{7,8} = x_{8,4} = 1
	\]
	
	All other variables are 0.
	}
	\item What is the total distance traveled by this solution?
	{
	\blu
	
	Total distance traveled is:
	\[
	5+1+7+1+8+7+2+2 = 33
	\]
	}
	\item Is this solution optimal for your TSP problem?
	{
	
	\blu
	No this is not the optimal solution. It consists of two cycles $1-2-5-6-1$ and $3-7-8-4-3$
	}
	\item If the solution is not optimal, write a constraint you could add to your model to remove this solution from your feasible region.
	{
	\blu
	
	I will write a constraint to eliminate the first cycle:
	\[
	x_{1,2}+x_{1,5}+x_{1,6} + x_{2,1}+x_{2,5}+x_{2,6} + x_{5,1}+x_{5,2}+x_{5,6} + x_{6,1}+x_{6,2}+x_{6,5} \leq 3
	\]
	}
	\end{enumerate}
\end{enumerate}


\end{document}
